---
title: "twitter-shiny"
author: "Shafayet Mannan"
date: "2023-02-02"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(rtweet, syuzhet, tidyverse, DT, stringr, wordcloud, tidytext)
```

## Introduction

This R Markdown document is made interactive using Shiny to demonstrate my abilities to make interactive data visualizations.

```{r load data, include=FALSE}
load('data.Rdata')
```

## Twitter data {.tabset}

### Recent Rstats tweets

The plot below shows time series of #rstats tweets and can be filtered by language.

```{r tweets, echo=FALSE}
inputPanel(
  selectInput("tweetlang", label = "Language of tweets:",
              choices = unique(tweets$lang), selected = "en", multiple = TRUE)
)

renderPlot({
  ts_plot(tweets %>% filter(lang %in% input$tweetlang), by = "hours", col = "blue") +
    labs(x = NULL, y = NULL, 
         title = "Frequency of tweets from containing #Rstats", 
         subtitle = paste0(format(min(tweets$created_at), "%d %B %Y")," to ", format(max(tweets$created_at), "%d %B %Y")), 
         caption = "Data collected from Twitter's REST API via rtweet") + theme_minimal()
})

renderDataTable({tweets %>%
    filter(lang %in% input$tweetlang) %>% 
    select(screen_name, text, lang, favorite_count, retweet_count)
  })
```

### Tweets from @RLadiesSeattle

The plots below show a wordle of terms, and a time series of tweets by @RLadiesSeattle. 
The time series can be plotted with different sources to see when different devices were used to tweet.

#### Time series plot of tweets

```{r user, echo=FALSE}
inputPanel(
  selectInput("tweetsource", label = "Source of tweets:",
              choices = unique(user_timeline$source), selected = unique(user_timeline$source), multiple = TRUE)
)

renderPlot({
  ts_plot(user_timeline %>% filter(source %in% input$tweetsource), by = "months", col = "blue") +
    labs(x = NULL, y = NULL,
       title = "Frequency of tweets from @RLadiesSeattle",
       subtitle = paste0(format(min(user_timeline$created_at), "%d %B %Y"), " to ", format(max(user_timeline$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via rtweet") + 
    theme_minimal()
})
```

